% !TEX encoding = UTF-8 Unicode
\documentclass[margin,line]{res}
%\usepackage{helvetica} 
%\usepackage{fontspec}
%\usepackage{newtxsf}
%\setmainfont{Helvetica}
\usepackage{hyperref}

\oddsidemargin -.7in
\evensidemargin -.5in
\textwidth=6in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{$\bullet$}{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}


\begin{document}
\name{\vspace*{-0.3in} \Large Mallory A Freeberg, Ph.D.} %Change to move name up/down

\begin{resume}
\section{\sc Contact}
\begin{tabular}{@{}p{3in}p{2.5in}}
Wellcome Trust Genome Campus & {\it Tw/GH}: @MalloryFreeberg \\
Hinxton, Cambridgeshire, CB10 1SD, UK &  {\it ORCID:} 0000-0003-2949-3921 \\
 {\it Email:}  mallory dot freeberg at gmail dot com &
\end{tabular}
%{\it Phone:}  + 44 (0) 1223 49 2567 &  {\it ORCID:} 0000-0003-2949-3921


%\section{\sc Research Interests}
%Genomics/genetics; post-transcriptional gene regulation; high-throughput technologies; second- and third-generation sequencing; data sharing and reuse; open-source tools and platforms enabling life sciences research

\section{\sc Professional Experience}
{\bf EMBL European Bioinformatics Institute}, Hinxton, UK\\
{\em Coordinator}, European Genome-phenome Archive \hfill {Jun 2021 - present}
\begin{itemize}
\itemsep0em 
	\item Manage day-to-day team operations to provide high-quality production services
	\item Engage with external partners and stakeholders to ensure data submission, discovery, and distribution services align with community standards
	\item Contribute expertise to help establish the Federated EGA network for transnational discovery of and access to sensitive human data
\end{itemize}

{\em UK Biobank Project Lead}, European Genome-phenome Archive \hfill {Aug 2019 - May 2021}
\begin{itemize}
\itemsep0em 
	\item Coordinated data flow to archive 500,000 whole human genomes (12PB of data)
	\item Led distribution of 4PB of data to cloud-based analysis platform
\end{itemize}

{\em Senior Bioinformatician}, Human Cell Atlas Data Coordination Platform \hfill {Oct 2018 - Jul 2019}
\begin{itemize}
\itemsep0em 
	\item Managed data wrangling tasks and priorities for six-person team across two institutions
	\item Represented HCA DCP by presenting at three international HCA meetings
\end{itemize}

{\em Bioinformatician}, Human Cell Atlas Data Coordination Platform \hfill {Oct 2017 - Sep 2018}
\begin{itemize}
\itemsep0em 
	\item Performed curation and ingestion of three flagship HCA datasets
	\item Developed HCA metadata standard for cellular-resolution transcriptomics data (\href{https://doi.org/10.1038/s41587-020-00744-z}{publication})
\end{itemize}

{\bf Johns Hopkins University}, Baltimore, MD USA\\
%{\bf The Galaxy Project}, Baltimore, MD USA\\
{\em Trainer}, Galaxy Training Network, The Galaxy Project \hfill {Jan 2017 - Sep 2017}
\begin{itemize}
\itemsep0em 
	\item Designed and delivered seven Galaxy training workshops in three countries (\href{https://doi.org/10.1016/j.cels.2018.05.012}{publication})
	\item Created training materials and computational workflows to support reproducible transcriptomics research (\href{https://training.galaxyproject.org/training-material/hall-of-fame/malloryfreeberg/}{contributions})
\end{itemize}

{\em Postdoctoral Research Fellow}, Department of Biology \hfill {Jun 2015 - Sep 2017}
\begin{itemize}
\itemsep0em 
	\item Investigated post-transcriptional gene regulatory networks using neural networks
	\item Piloted Oxford Nanopore direct RNA sequencing protocols to catalog transcriptomes
\end{itemize}

%Advisor:  Dr. James Taylor

%{\bf University of Michigan}, Ann Arbor, MI USA\\
%{\em Graduate Student} \hfill {Jul 2009 - May 2015}\\
%Dissertation: Computational analysis of the post-transcriptional gene regulatory network\\
%Advisor:  Dr. John K. Kim

%{\bf Saint Vincent College}, Latrobe, PA USA\\
%{\em Undergraduate Student} \hfill {Jan 2008 - May 2009}\\
%Dissertation: Functional annotation of non-coding elements in the Amphioxus genome\\
%Advisor:  Dr. Michael L. Sierk\\

%{\bf Boyce Thompson Institute for Plant Research}, Ithaca, NY USA\\
%{\em Summer Research Intern} \hfill {May - Aug 2008}\\
%Research: Designed and implemented a motif discovery tool to identify conserved DNA motifs in untranslated gene regions from plants in the {\em Solanaceae} family\\
%Research: Developed computational tool to discover conserved motifs in {\em Solanaceae} genomes\\
%Advisor: Dr. Lukas A. Mueller

%{\bf Johns Hopkins University Applied Physics Laboratory}, Laurel, MD USA\\
%{\em Summer Research Intern} \hfill {May - Aug 2007}\\
%Research: Developed pipeline and built database to identify microorganisms in an environmental sample by comparing mass spectrometry spectral peak data to known protein molecular weights\\
%Research: Designed computational pipeline for microorganism identification by mass spectrometry\\
%Advisors: Drs. Plamen A. Demirev and Richard S. Potember

%{\bf Saint Vincent College}, Latrobe, PA USA\\
%{\em Summer Research Intern} \hfill {May - Aug 2006}\\
%Evaluated the effectiveness of protein databases to classify protein domains using pairwise-, profile-, and structure-based alignment algorithms\\
%Advisor: Dr. Michael L. Sierk

\section{\sc Education}
{\bf Ph.D. Bioinformatics}, University of Michigan, USA \hfill {May 2015}\\
Department of Computational Medicine and Bioinformatics\\ 
Dissertation: Computational analysis of the post-transcriptional gene regulatory network

{\bf B.S. Bioinformatics}, Saint Vincent College, USA \hfill {May 2009}\\
Herbert M. Boyer School of Natural Science, Mathematics, and Computing\\
Dissertation: Functional annotation of non-coding elements in the Amphioxus genome
%{Minors: Biochemistry, Computing/Information Sciences}

\section{\sc Training\\ Courses}

EMBL-EBI Storytelling Workshop \hfill {Jul 2021}\\
EMBL-EBI Managing Managers Course \hfill {Apr 2021}\\
EMBL-EBI Moving into Management Course \hfill {Sep 2020 - Oct 2020}\\
%EMBL-EBI Emotional Intelligence and Mindfulness Course \hfill {Apr 2020}\\
Talented Women's Impact Programme \hfill {Sep 2019 - Jan 2020}\\
EICAT Complementary Scientific Skills Training - Scientific Project Management \hfill {Sep 2019}\\
Handling Conflict and Difficult Conversations \hfill {Sep 2018}

\section{\sc Selected Invited Talks}

% {\bf Freeberg MA} and AUTHORS. Title. {\em Conference}; MMM YYYY; (Venue), City, State/Country

{\bf Freeberg MA}. FAIR principles and promoting openness in the life sciences. {\em NIHR Statistics Group Workshop}; Feb 2022; Virtual

{\bf Freeberg MA}. The EGA Metadata Model. {\em GHGA Workshop on Metadata in Biomedical Genome Research}; Jun 2021; Virtual

{\bf Freeberg MA}, Yordanova G, and Tickle T. How to engage with the Data Coordination Platform. {\em Human Cell Atlas General Meeting}; May 2019; Toyko, Japan

Clarke L, {\bf Freeberg MA}, and Yordonova G. Human Cell Atlas Data Coordination Platform. {\em Pilot Projects for a Human Cell Atlas Europe Retreat}; Aug 2018; Stockholm, Sweden

%{\bf Freeberg MA}. Human Cell Atlas: Google Maps for human anatomy. Cambridge UK Computational Biology and Bioinformatics Meetup; Jun 2018; Cambridge, UK

Clarke L, {\bf Freeberg MA}, O'Connor B, Osborn K, and Tickle T. Human Cell Atlas Data Coordination Platform: Status Update. {\em Human Cell Atlas General Meeting}; Mar 2018; Hinxton, UK

% {\bf Freeberg MA}. Single molecule RNA sequencing of the {\em C. elegans} transcriptome. {\em Molecular Biosystems Conference on Eukaryotic Gene Regulation and Functional Genomics}; Sep 2017; Puerto Varas, Chile. Sponsored by Oxford Nanopore Technologies

%{\bf Freeberg MA}. From high school to postdoc: lessons from a decade of bioinformatics education. Great Lakes Bioinformatics Conference; May 2017; University of Illinois at Chicago, Chicago, IL. DOI:10.7490/f1000research.1114161.1

%{\bf Freeberg MA}. A novel pipeline for identifying transcriptome-wide binding sites of RNA-binding proteins from PAR-CLIP sequencing data. NCIBI Tools and Technology Seminar Series; May 2013; University of Michigan, Ann Arbor, MI
%{\bf Freeberg MA} and Stevenson KR. Recommendations for successful scientific data sharing: Case studies of next-generation sequencing data use and re-use. NSF Open Data IGERT Seminar; Mar 2013; University of Michigan, Ann Arbor, MI\\
%{\bf Freeberg MA}. Defending the genome: Computational identification of germline-specific piRNAs in {\em C. elegans}. Sep 2012; Saint Vincent College, Latrobe, PA
%{\bf Freeberg MA}. Next-generation sequencing data re-use facilitates studies of small RNAs. NSF Open Data IGERT Research Workshop; Apr 2012; University of Michigan, Ann Arbor, MI\\

\section{\sc Selected Publications}

{\bf Freeberg MA}, Fromont L., D'Altri T, Romero AF, Ciges JI, Jene A, Kerry G, Moldes M, Ariosa R, Bahena S, {\em et al.} (2021) The European Genome-phenome Archive in 2021. {\em Nucleic Acids Res}, 2021. DOI:10.1093/nar/gkab1059

Rehm HL, Page AJH, Smith L, Adams JB, Alterovitz G, Babb LJ, Barkley MP, Baudis M, Beauvais MJS, Beck T, {\em et al.} (2021) GA4GH: International policies and standards for data sharing across genomic research and healthcare. {\em Cell Genomics} 1. DOI:10.1016/j.xgen.2021.100029

Lawson J, Cabili MN, Kerry G, Boughtwood T, Thorogood A, Alper P, Bowers SR, Boyles RR, Brookes AJ, Brush M, {\em et al.} (2021) The Data Use Ontology to streamline responsible access to human biomedical datasets. {\em Cell Genomics} 1. DOI:10.1016/j.xgen.2021.100028

Füllgrabe A, George N, Green M, Nejad P, Aronow B, Fexova SK, Fischer C, {\bf Freeberg MA}, Huerta L, Morrison N, Scheuermann RH, Taylor D, Vasilevsky N, Clarke L, Gehlenborg N, Kent J, Marioni J, Teichmann S, Brazma A, Papatheodorou I. (2020) Guidelines for reporting single-cell RNA-seq experiments. {\em Nat Biotechnol} 38:1384-6. DOI:10.1038/s41587-020-00744-z ({\em arXiv} preprint DOI:1910.14623v1)

Batut B, Hiltemann S, Bagnacani A, Baker D, Bhardwaj V, Blank C, Bretaudeau A, Brillet-Guéguen L, Cech M, Chilton J, Clements D, Doppelt-Azeroual O, Erxleben A, {\bf Freeberg MA}, {\em et al.} (2018) Community-Driven Data Analysis Training for Biology. {\em Cell Syst} 6(6):752-758. DOI:10.1016/j.cels.2018.05.012 ({\em bioRxiv} preprint DOI:10.1101/225680)

\section{\sc Teaching and Mentoring Experience}
{\bf Open Life Science}, Cambridge, UK\hfill {Jul 2020 - Present}\\
Mentor, 16-week personal mentorship and cohort-based training program\\
Responsibilities: Mentoring participants on open science practices

{\bf STEM Ambassador}, Cambridge, UK\hfill {Jan 2018 - Present}\\
Ambassador, STEM-related public engagment program\\
Responsibilities: Giving talks, demonstrating science experiments, providing career guidance

{\bf Johns Hopkins University}, Baltimore, MD USA\hfill {Jan 2017 - May 2017}\\
Instructor, Advanced Academic Program online course: {\em Bioinformatics: Tools for Genome Analysis}\\
Responsibilities: Created course materials, held office hours, graded assignments

%{\bf Sisters Circle}, Baltimore, MD USA\hfill {May 2015 - Sep 2017}\\
%Mentor/tutor for middle school girls\\
%Responsibilities: Co-led weekly after-school sessions, tutored math, mentored 1-on-1

%{\bf University of Michigan}, Ann Arbor, MI USA\hfill {Jul 2014 - Aug 2014}\\
%Mentor for high school student\\
%Responsibilities: Designed bioinformatics/genomics research project, taught shell/perl programming

%{\bf Saint Vincent College}, Latrobe, PA USA\\
%Laboratory Assistant for General Chemistry \hfill { Jan - May 2009}\\
%Responsibilities: Held office hours, prepared and supervised laboratory exercises, graded assignments

%Laboratory Assistant for Genes, Cells, and Computers \hfill { Aug - Dec 2008}\\
%Responsibilities: Held office hours, prepared and supervised laboratory exercises, graded assignments

%Tutor for Bioinformatics, Genomics, and Proteomics \hfill { Aug - Dec 2007}\\
%Responsibilities: Held office hours, led study sessions

\section{\sc Conferences\\ and Workshops}

Bacon W, Morgan S, Welter D, and {\bf Freeberg MA}. Managing single cell transcriptomics data. EMBL Course; Jul 2019; Cambridge, UK (Workshop)

{\bf Freeberg MA}. The Data Coordination Platform: Making the Human Cell Atlas data easily accessible. The Biology of Genomes; May 2018; Cold Spring Harbor, NY (Poster)

{\bf Freeberg MA}. Single molecule RNA sequencing of the {\em C. elegans} transcriptome. {\em Molecular Biosystems Conference on Eukaryotic Gene Regulation and Functional Genomics}; Sep 2017; Puerto Varas, Chile. Sponsored by Oxford Nanopore Technologies (Talk)

{\bf Freeberg MA} and Taylor J. Approaches for small RNA-seq in Galaxy. Galaxy Community Conference; Jun 2017; Montpellier, France (Talk)
DOI:10.7490/f1000research.1114423.1

%{\bf Freeberg MA} and Heydarian M. Galaxy 101: A gentle introduction to Galaxy. Galaxy Community Conference; Jun 2017; Montpellier, France (Workshop)

{\bf Freeberg MA} and Heydarian M. RNAseq analysis in Galaxy. Galaxy Community Conference; Jun 2017; Montpellier, France (Workshop)

{\bf Freeberg MA} and Heydarian M. Introduction to Genomic Data Analysis with Galaxy. U. S. Food and Drug Administration; Mar 2017; Silver Spring, MD, USA (Workshop)

%{\bf Freeberg MA} and Heydarian M. Introduction to Genomic Data Analysis with Galaxy. Global Biodiversity Genomics Conference; Feb 2017; Washington D.C. (Workshop)

{\bf Freeberg MA} and Heydarian M. Galaxy to Genomics using NGS Data. 13th KOGO Winter Symposium; Feb 2017; Hongcheon, South Korea (Workshop)

%{\bf Freeberg MA} and Heydarian M. Galaxy to Genomics using NGS Data. Feb 2017; Daejeon and Seoul, South Korea (Workshops)

{\bf Freeberg MA} and Turaga N. Bioinformagic: Marrying Bioconductor and Galaxy. Galaxy Community Conference; Jun 2016; Bloomington, IN, USA (Workshop)

{\bf Freeberg MA}. Transcriptome sequencing in nematodes. Oxford Nanopore Technologies London Calling; May 2016; London, UK (Poster)

{\bf Freeberg MA} and Taylor J. Probabilistic modeling of protein:RNA interaction data identifies functional Transcript States. CSHL Genome Informatics; Oct 2015; Cold Spring Harbor, NY (Poster)

{\bf Freeberg MA}. Identification and characterization of the mRNA-binding proteome {\em in vivo} in {\em Saccharomyces cerevisiae}. CSHL Systems Biology: Global Regulation of Gene Expression; Mar 2014; Cold Spring Harbor, NY (Talk)

% {\bf Freeberg MA}, Billi AC, and Kim JK. Germline expression, inheritance, and genomic characteristics of {\em Caenorhabditis elegans} 21U-RNAs. 18th International {\em C. elegans} Meeting; Jun 2011; Los Angeles, CA (Poster)

% {\bf Freeberg MA}. Functional Annotation of Non-Coding Elements in the Amphioxus Genome. Saint Vincent College 6th Annual Undergraduate Conference; Apr 2009; Latrobe, PA. (Talk)\\

% {\bf Freeberg MA} and Demirev PA. Bioinformatics Approach to Protein Database Generation for the Identification of Microorganisms by Mass Spectrometry. Saint Vincent College 5th Annual Undergraduate Conference; Apr 2008; Latrobe, PA. (Poster)

% {\bf Freeberg MA} and Sierk ML. Assessment of Homolog Detection by Profile-based Protein Sequence Alignment Methods Against a Structure-based Gold Standard. Duquesne University Annual Summer Undergraduate Research Symposium; Aug 2006; Pittsburgh, PA. (Poster)

\section{\sc Other Publications}

Fuller GG, Han T, {\bf Freeberg MA}, Moresco JJ, Niaki AG, Roach NP,Yates III JR, Myong S, Kim JK. (2020) RNA promotes phase separation of glycolysis enzymes into yeast G bodies in hypoxia. {\em eLife} 2020;9:e48480. DOI:10.7554/eLife.48480 ({\em bioRxiv} preprint DOI:10.1101/638650)

Gruning B, Dale R, Sjodin A, Chapman BA, Rowe J, Tomkins-Tinch CH, Valieris R, Koster J, {\bf The Bioconda Team}. (2018) Bioconda: sustainable and comprehensive software distribution for the life sciences. {\em Nat Meth} 15:475-6. DOI:10.1038/s41592-018-0046-7 ({\em bioRxiv} preprint DOI:10.1101/207092)

Lariviere D, Mei H, {\bf Freeberg MA}, Taylor J, Nekrutenko A. (2018) Understanding trivial challenges of microbial genomics: An assembly example. {\em bioRxiv} (preprint) 347625. DOI:10.1101/347625

Malhotra S, {\bf Freeberg MA}, Winans SJ, Taylor J, Beemon KL. (2018) A Novel Long Non-Coding RNA in the {\em hTERT} Promoter Region Regulates {\em hTERT} Expression. {\em Non-Coding RNA} 4(1). DOI:10.3390/ncrna4010001

Hong S, {\bf Freeberg MA}*, Han T*, Kamath A*, Yao Y, Fukuda T, Suzuki T, Kim JK, and Inoki K. (2017) LARP-1 functions as a molecular switch for mTORC1-mediated translation of an essential class of mRNAs. {\em eLife} 6:e25237. DOI:10.7554/eLife.25237

Jin M*, Fuller GG*, Han T*, Yao Y, Alessi AF, {\bf Freeberg MA}, Roach NP, Moresco JJ, Karnovsky A, Baba M, Yates JR III, Gitler AD, Inoki K, Klionsky DJ, Kim JK. (2017) Glycolytic Enzymes Coalesce in G Bodies Under Hypoxic Stress. {\em Cell Reports} 20(4):895-908. DOI:10.1016/j.celrep.2017.06.082

Weiser NE, Yang DX, Feng S, Kalinava N, Brown KC, Khanikar J, {\bf Freeberg MA}, Snyder MJ, Csankovszki G, Chan RC,  Gu SG, Montgomery TA, Jacobsen SE, and Kim JK. (2017) MORC-1 Integrates Nuclear RNAi and Transgenerational Chromatin Architecture to Promote Germline Immortality. {\em Dev Cell} 41(4):408-23. DOI:10.1016/j.devcel.2017.04.023

%Turaga N, {\bf Freeberg MA}, Baker D, Chilton J, The Galaxy Team, Nekrutenko A, and Taylor J. (2016) A guide and best practices for R/Bioconductor tool integration in Galaxy [version 1; referees: 1 approved, 1 approved with reservations]. {\em F1000Research} 5:2757. DOI:10.12688/f1000research.9821.1

{\bf Freeberg MA} and Kim JK. (2016) Mapping the Transcriptome-Wide Landscape of RBP Binding Sites using gPAR-CLIP-seq: Bioinformatic Analysis. Invited chapter in {\em Methods in Mol Biol} 1361(6):91-104. DOI:10.1007/978-1-4939-3079-1

Alessi AF*, Khivansara V*, Han T*, {\bf Freeberg MA}, Moresco JJ, Tu PG, Montoye E, Yates JR III, Karp X, and Kim JK. (2015) Casein kinase II promotes target silencing by miRISC through direct phosphorylation of the DEAD-box RNA helicase CGH-1. {\em PNAS} 112(49):E6789. \\DOI:10.1073/pnas.1509499112

Jin M, He D, Backues SK, {\bf Freeberg MA}, Liu X, Kim JK, and Klionsky DJ. (2014) Transcriptional regulation by Pho23 modulates the frequency of autophagosome formation. {\em Curr Biol} 24(12):1314-22. DOI:10.1016/j.cub.2014.04.048

{\bf Freeberg MA}*, Han T*, Moresco JJ, Kong A, Yang Y, Lu Z, Yates JR III, and Kim JK. (2013) Pervasive and dynamic protein binding sites on the mRNA transcriptome in {\em Saccharomyces cerevisiae}. {\em Gen Biol} 14(2):R13. DOI:10.1186/gb-2013-14-2-r13

Billi AC*, {\bf Freeberg MA}*, Day AM, Chun SY, Khivansara V, and Kim JK. (2013) A conserved upstream motif drives autonomous, germline-enriched expression of {\em Caenorhabditis elegans} piRNAs. {\em PLoS Genet} 9(3):e1003392. DOI:10.1371/journal.pgen.1003392

Billi AC, {\bf Freeberg MA}, and Kim JK. (2012) piRNAs and siRNAs collaborate in {\em Caenorhabditis elegans} genome defense. {\em Gen Biol} 13(7):164. DOI:10.1186/gb-2012-13-7-164

Billi AC, Alessi AF, Khivansara V, Han T, {\bf Freeberg M}, Mitani S, and Kim JK. (2012) The {\em Caenorhabditis elegans} HEN1 ortholog, HENN-1, methylates and stabilizes select subclasses of germline small RNAs. {\em PLoS Genet} 8(4):e1002617. DOI:10.1371/journal.pgen.1002617

*equal contribution

\section{\sc Funding} 
%{\bf University of Michigan}\\
{XSEDE Educational Computational Resource Allocation (2017)}\\
{XSEDE Startup Computational Resource Allocation (2017)}\\
%{Galaxy Community Fund, Travel Award (2017)}\\
%{Rackham Conference Travel Grant (2014)}\\
{Rackham Predoctoral Fellowship (2013-2014)}\\
{NSF Open Data IGERT Fellowship (2010-2013)}\\
{Rackham Graduate Student Research Grant (2010, 2012)}\\
{NIH Bioinformatics Training Grant (2009-2010)}\\

%\vspace{-.2cm}
%{\bf Saint Vincent College}\\
%{Graduated Summa Cum Laude, 2009}\\
%{President's Award Finalist, 2009}\\
%{Outstanding Bioinformatics Student Award, 2009}
%{Who's Who Among Students in American Universities and Colleges   2009}\\
%{Alpha Lambda Delta Academic Honor Society 2006-2009}

%\section{\sc Computing and Data Analysis Skills} 
%Operating Systems: MacOS X, Linux/Unix \\
%Languages: Python, Perl, SQL, Unix shell \\
%Statistical Packages: R, Bioconductor \\
%Applications: JSON/XML, GitHub, \LaTeX, Galaxy, NGS analysis tools and methodologies\\

%Applications: \LaTeX, MySQL, Galaxy, biomolecule sequence/structure analysis tools, NGS analysis tools and methodologies\\
%Laboratory Techniques: Nanopore sequencing, general molecular biology techniques\\
%Laboratory Techniques: Nanopore sequencing (Oxford Nanopore Technologies), general molecular biology techniques

%\section{\sc University and Community Service}
%%{Volunteered for FEMMES Capstone Science weekend}\\
%%{Judged Pioneer High School Science Fair, 2014}\\
%%{Judged Forsythe Middle School Science Fair, 2014}\\
%{Peer reviewed for {\em Cell Rep},  {\em Epigenetics}, {\em Genome Biol}, {\em Genome Res}, {\em PLoS Biol}, {\em RNA}, and {\em RNA Biol} (2013-2014)}\\
%%{Judged Webster Elementary School Science Fair and Exhibition, 2013-2014}\\
%%{Organized departmental happy hours following student seminars, 2012-2014}\\
%{Participated in departmental student recruiting activities, University of Michigan (2011-2015)}\\
%%{Judged Elementary, Middle, and High School Science Fairs, 2013-2014}

\end{resume}
\end{document}

