% !TEX encoding = UTF-8 Unicode
\documentclass[margin,line]{res}
%\usepackage{helvetica} 
%\usepackage{fontspec}
%\usepackage{newtxsf}
%\setmainfont{Helvetica}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{$\bullet$}{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}


\begin{document}
\name{\vspace*{-0.3in} \Large Mallory A Freeberg, Ph.D.} %Change to move name up/down

\begin{resume}
\section{\sc Contact Information}
\begin{tabular}{@{}p{2.5in}p{5in}}
Wellcome Trust Genome Campus & {\it Email:}  mallory dot freeberg at gmail dot com \\
Hinxton, Cambridgeshire, CB10 1SD, UK & {\it Tw/GH}: @MalloryFreeberg \\
{\it Phone:}  + 44 (0) 1223 49 2567 &  {\it ORCID:} 0000-0003-2949-3921
\end{tabular}

%\section{\sc Research Interests}
%Genomics/genetics; post-transcriptional gene regulation; high-throughput technologies; second- and third-generation sequencing; data sharing and reuse; open-source tools and platforms enabling life sciences research

\section{\sc Education}
{\bf University of Michigan}, Ann Arbor, MI USA\\
{\em Department of Computational Medicine and Bioinformatics}\\ 
{Ph.D. Bioinformatics, May 2015}\\
Dissertation: Computational analysis of the post-transcriptional gene regulatory network

{\bf Saint Vincent College}, Latrobe, PA USA\\
{\em Herbert M. Boyer School of Natural Science, Mathematics, and Computing} \\
{B.S. Bioinformatics,  May 2009}\\
Dissertation: Functional annotation of non-coding elements in the Amphioxus genome\\

%{Minors: Biochemistry, Computing/Information Sciences}

\section{\sc Research and Work Experience}
{\bf EMBL European Bioinformatics Institute}, Hinxton, Cambridgeshire UK\\
{\em Project Lead, European Genome-phenome Archive} \hfill {Aug 2019 - present}\\
Coordinating archive and distribution of 500,000 UK Biobank whole genome sequences

{\em Senior Bioinformatician, Human Cell Atlas Data Coordination Platform} \hfill {Oct 2018 - Jul 2019}\\
Developed metadata standards for cellular-resolution genomics data and managed data ingestion

{\em Bioinformatician, Human Cell Atlas Data Coordination Platform} \hfill {Oct 2017 - Sep 2018}\\
Developed metadata standards for cellular-resolution genomics data and performed data ingestion

{\bf Johns Hopkins University}, Baltimore, MD USA\\
%{\bf The Galaxy Project}, Baltimore, MD USA\\
{\em Team Member, The Galaxy Project} \hfill {Jan 2017 - Sep 2017}\\
Developed workflows, training materials, and best practices for transcriptomics \& genomics research

{\em Postdoctoral Research Fellow, Department of Biology} \hfill {Jun 2015 - Sep 2017}\\
Investigated post-transcriptional gene regulatory networks and developed nanopore direct RNA sequencing protocols\\
%Advisor:  Dr. James Taylor

%{\bf University of Michigan}, Ann Arbor, MI USA\\
%{\em Graduate Student} \hfill {Jul 2009 - May 2015}\\
%Dissertation: Computational analysis of the post-transcriptional gene regulatory network\\
%Advisor:  Dr. John K. Kim

%{\bf Saint Vincent College}, Latrobe, PA USA\\
%{\em Undergraduate Student} \hfill {Jan 2008 - May 2009}\\
%Dissertation: Functional annotation of non-coding elements in the Amphioxus genome\\
%Advisor:  Dr. Michael L. Sierk\\

%{\bf Boyce Thompson Institute for Plant Research}, Ithaca, NY USA\\
%{\em Summer Research Intern} \hfill {May - Aug 2008}\\
%Research: Designed and implemented a motif discovery tool to identify conserved DNA motifs in untranslated gene regions from plants in the {\em Solanaceae} family\\
%Research: Developed computational tool to discover conserved motifs in {\em Solanaceae} genomes\\
%Advisor: Dr. Lukas A. Mueller

%{\bf Johns Hopkins University Applied Physics Laboratory}, Laurel, MD USA\\
%{\em Summer Research Intern} \hfill {May - Aug 2007}\\
%Research: Developed pipeline and built database to identify microorganisms in an environmental sample by comparing mass spectrometry spectral peak data to known protein molecular weights\\
%Research: Designed computational pipeline for microorganism identification by mass spectrometry\\
%Advisors: Drs. Plamen A. Demirev and Richard S. Potember

%{\bf Saint Vincent College}, Latrobe, PA USA\\
%{\em Summer Research Intern} \hfill {May - Aug 2006}\\
%Evaluated the effectiveness of protein databases to classify protein domains using pairwise-, profile-, and structure-based alignment algorithms\\
%Advisor: Dr. Michael L. Sierk

\section{\sc Publications}

Füllgrabe A, George N, Green M, Nejad P, Aronow B, Clarke L, Fexova SK, Fischer C, {\bf Freeberg MA}, Huerta L, Morrison N, Scheuermann RH, Taylor D, Vasilevsky N, Gehlenborg N, Marioni J, Teichmann S, Brazma A, Papatheodorou I. (2019) Guidelines for reporting single-cell RNA-Seq experiments. {\em arXiv} (preprint) 1910.14623v1.

Fuller GG, Han T, {\bf Freeberg MA}, Moresco JJ, Niaki AG, Roach NP,Yates III JR, Myong S, Kim JK. (2020) RNA promotes phase separation of glycolysis enzymes into yeast G bodies in hypoxia. {\em eLife} 2020;9:e48480. DOI:10.7554/eLife.48480 ({\em bioRxiv} preprint DOI:10.1101/638650)

%Fuller GG, Han T, {\bf Freeberg MA}, Moresco JJ, Yates III JR, Kim JK. (2019) RNA promotes phase separation of glycolysis enzymes into yeast G bodies in hypoxia. {\em bioRxiv} (preprint) 638650. DOI:10.1101/638650

Batut B, Hiltemann S, Bagnacani A, Baker D, Bhardwaj V, Blank C, Bretaudeau A, Brillet-Guéguen L, Cech M, Chilton J, Clements D, Doppelt-Azeroual O, Erxleben A, {\bf Freeberg MA}, {\em et al.} (2018) Community-Driven Data Analysis Training for Biology. {\em Cell Syst} 6(6):752-758. DOI:10.1016/j.cels.2018.05.012 ({\em bioRxiv} preprint DOI:10.1101/225680)

Lariviere D, Mei H, {\bf Freeberg MA}, Taylor J, Nekrutenko A. (2018) Understanding trivial challenges of microbial genomics: An assembly example. {\em bioRxiv} (preprint) 347625. DOI:10.1101/347625

Gruning B, Dale R, Sjodin A, Chapman BA, Rowe J, Tomkins-Tinch CH, Valieris R, Koster J, {\bf The Bioconda Team}. (2018) Bioconda: sustainable and comprehensive software distribution for the life sciences. {\em Nat Meth} 15:475-6. DOI:10.1038/s41592-018-0046-7 ({\em bioRxiv} preprint DOI:10.1101/207092)

Malhotra S, {\bf Freeberg MA}, Winans SJ, Taylor J, Beemon KL. (2018) A Novel Long Non-Coding RNA in the {\em hTERT} Promoter Region Regulates {\em hTERT} Expression. {\em Non-Coding RNA} 4(1). DOI:10.3390/ncrna4010001

%Dale R, Grüning B, Sjödin A, Rowe J, Chapman BA, Tomkins-Tinch CH, Valieris R, {\bf The Bioconda Team}, Köster J. (2017) Bioconda: A sustainable and comprehensive software distribution for the life sciences. {\em bioRxiv} (preprint) 207092. DOI:10.1101/207092

Hong S, {\bf Freeberg MA}*, Han T*, Kamath A*, Yao Y, Fukuda T, Suzuki T, Kim JK, and Inoki K. (2017) LARP-1 functions as a molecular switch for mTORC1-mediated translation of an essential class of mRNAs. {\em eLife} 6:e25237. DOI:10.7554/eLife.25237

Jin M*, Fuller GG*, Han T*, Yao Y, Alessi AF, {\bf Freeberg MA}, Roach NP, Moresco JJ, Karnovsky A, Baba M, Yates JR III, Gitler AD, Inoki K, Klionsky DJ, Kim JK. (2017) Glycolytic Enzymes Coalesce in G Bodies Under Hypoxic Stress. {\em Cell Reports} 20(4):895-908. DOI:10.1016/j.celrep.2017.06.082

Weiser NE, Yang DX, Feng S, Kalinava N, Brown KC, Khanikar J, {\bf Freeberg MA}, Snyder MJ, Csankovszki G, Chan RC,  Gu SG, Montgomery TA, Jacobsen SE, and Kim JK. (2017) MORC-1 Integrates Nuclear RNAi and Transgenerational Chromatin Architecture to Promote Germline Immortality. {\em Dev Cell} 41(4):408-23. DOI:10.1016/j.devcel.2017.04.023

Turaga N, {\bf Freeberg MA}, Baker D, Chilton J, The Galaxy Team, Nekrutenko A, and Taylor J. (2016) A guide and best practices for R/Bioconductor tool integration in Galaxy [version 1; referees: 1 approved, 1 approved with reservations]. {\em F1000Research} 5:2757. DOI:10.12688/f1000research.9821.1

{\bf Freeberg MA} and Kim JK. (2016) Mapping the Transcriptome-Wide Landscape of RBP Binding Sites using gPAR-CLIP-seq: Bioinformatic Analysis. Invited chapter in {\em Methods in Mol Biol} 1361(6):91-104. DOI:10.1007/978-1-4939-3079-1

Alessi AF*, Khivansara V*, Han T*, {\bf Freeberg MA}, Moresco JJ, Tu PG, Montoye E, Yates JR III, Karp X, and Kim JK. (2015) Casein kinase II promotes target silencing by miRISC through direct phosphorylation of the DEAD-box RNA helicase CGH-1. {\em PNAS} 112(49):E6789. \\DOI:10.1073/pnas.1509499112

Jin M, He D, Backues SK, {\bf Freeberg MA}, Liu X, Kim JK, and Klionsky DJ. (2014) Transcriptional regulation by Pho23 modulates the frequency of autophagosome formation. {\em Curr Biol} 24(12):1314-22. DOI:10.1016/j.cub.2014.04.048

{\bf Freeberg MA}*, Han T*, Moresco JJ, Kong A, Yang Y, Lu Z, Yates JR III, and Kim JK. (2013) Pervasive and dynamic protein binding sites on the mRNA transcriptome in {\em Saccharomyces cerevisiae}. {\em Gen Biol} 14(2):R13. DOI:10.1186/gb-2013-14-2-r13

Billi AC*, {\bf Freeberg MA}*, Day AM, Chun SY, Khivansara V, and Kim JK. (2013) A conserved upstream motif drives autonomous, germline-enriched expression of {\em Caenorhabditis elegans} piRNAs. {\em PLoS Genet} 9(3):e1003392. DOI:10.1371/journal.pgen.1003392
%Comment in: Burgess DJ. (2013) Small RNAs: Defining piRNA expression. {\em Nat Rev Genet} 14(5):301.

Billi AC, {\bf Freeberg MA}, and Kim JK. (2012) piRNAs and siRNAs collaborate in {\em Caenorhabditis elegans} genome defense. {\em Gen Biol} 13(7):164. DOI:10.1186/gb-2012-13-7-164

Billi AC, Alessi AF, Khivansara V, Han T, {\bf Freeberg M}, Mitani S, and Kim JK. (2012) The {\em Caenorhabditis elegans} HEN1 ortholog, HENN-1, methylates and stabilizes select subclasses of germline small RNAs. {\em PLoS Genet} 8(4):e1002617. DOI:10.1371/journal.pgen.1002617

*equal contribution

\section{\sc Invited Talks}

% {\bf Freeberg MA} and AUTHORS. Title. Conference; MMM YYYY; (Venue), City, State/Country

{\bf Freeberg MA}, Yordanova G, and Tickle T. How to engage with the Data Coordination Platform. Human Cell Atlas General Meeting; May 2019; Toyko, Japan

Clarke L, {\bf Freeberg MA}, and Yordonova G. Human Cell Atlas Data Coordination Platform. Pilot Projects for a Human Cell Atlas Europe Retreat; Aug 2018; Stockholm, Sweden

%{\bf Freeberg MA}. Human Cell Atlas: Google Maps for human anatomy. Cambridge UK Computational Biology and Bioinformatics Meetup; Jun 2018; Cambridge, UK

Clarke L, {\bf Freeberg MA}, O'Connor B, Osborn K, and Tickle T. Human Cell Atlas Data Coordination Platform: Status Update. Human Cell Atlas General Meeting; Mar 2018; Hinxton, UK

{\bf Freeberg MA}. Single molecule RNA sequencing of the {\em C. elegans} transcriptome. Molecular Biosystems Conference on Eukaryotic Gene Regulation and Functional Genomics; Sep 2017; Puerto Varas, Chile. Sponsored by Oxford Nanopore Technologies

{\bf Freeberg MA}. From high school to postdoc: lessons from a decade of bioinformatics education. Great Lakes Bioinformatics Conference; May 2017; University of Illinois at Chicago, Chicago, IL. DOI:10.7490/f1000research.1114161.1
%{\bf Freeberg MA}. From high school to postdoc: Lessons from a decade of bioinformatics education [version 1; not peer reviewed]. {\em F1000Research} 2017, {\bf 6}(ISCB Comm J):801. DOI:10.7490/f1000research.1114161.1

{\bf Freeberg MA}. A novel pipeline for identifying transcriptome-wide binding sites of RNA-binding proteins from PAR-CLIP sequencing data. NCIBI Tools and Technology Seminar Series; May 2013; University of Michigan, Ann Arbor, MI

%{\bf Freeberg MA} and Stevenson KR. Recommendations for successful scientific data sharing: Case studies of next-generation sequencing data use and re-use. NSF Open Data IGERT Seminar; Mar 2013; University of Michigan, Ann Arbor, MI\\

%{\bf Freeberg MA}. Defending the genome: Computational identification of germline-specific piRNAs in {\em C. elegans}. Sep 2012; Saint Vincent College, Latrobe, PA

%{\bf Freeberg MA}. Next-generation sequencing data re-use facilitates studies of small RNAs. NSF Open Data IGERT Research Workshop; Apr 2012; University of Michigan, Ann Arbor, MI\\

\section{\sc Conference\\ Talks and Workshops}

{\bf Freeberg MA}. The Data Coordination Platform: Making the Human Cell Atlas data easily accessible. The Biology of Genomes; May 2018; Cold Spring Harbor, NY (Poster)

{\bf Freeberg MA} and Taylor J. Approaches for small RNA-seq in Galaxy [version 1; not peer reviewed]. Galaxy Community Conference; Jun 2017; Montpellier, France (Talk)
{\em F1000Research} 6:1137. DOI:10.7490/f1000research.1114423.1

%{\bf Freeberg MA} and Heydarian M. Galaxy 101: A gentle introduction to Galaxy. Galaxy Community Conference; Jun 2017; Montpellier, France (Workshop)

{\bf Freeberg MA} and Heydarian M. RNAseq analysis in Galaxy. Galaxy Community Conference; Jun 2017; Montpellier, France (Workshop)

{\bf Freeberg MA} and Heydarian M. Introduction to Genomic Data Analysis with Galaxy. U. S. Food and Drug Administration; Mar 2017; Silver Spring, MD, USA (Workshop)

%{\bf Freeberg MA} and Heydarian M. Introduction to Genomic Data Analysis with Galaxy. Global Biodiversity Genomics Conference; Feb 2017; Washington D.C. (Workshop)

{\bf Freeberg MA} and Heydarian M. Galaxy to Genomics using NGS Data. 13th KOGO Winter Symposium; Feb 2017; Hongcheon, South Korea (Workshop)

%{\bf Freeberg MA} and Heydarian M. Galaxy to Genomics using NGS Data. Feb 2017; Daejeon and Seoul, South Korea (Workshops)

{\bf Freeberg MA} and Turaga N. Bioinformagic: Marrying Bioconductor and Galaxy. Galaxy Community Conference; Jun 2016; Bloomington, IN, USA (Workshop)

{\bf Freeberg MA}. Transcriptome sequencing in nematodes. Oxford Nanopore Technologies London Calling; May 2016; London, UK (Poster)

{\bf Freeberg MA} and Taylor J. Probabilistic modeling of protein:RNA interaction data identifies functional Transcript States. CSHL Genome Informatics; Oct 2015; Cold Spring Harbor, NY (Poster)

{\bf Freeberg MA}. Identification and characterization of the mRNA-binding proteome {\em in vivo} in {\em Saccharomyces cerevisiae}. CSHL Systems Biology: Global Regulation of Gene Expression; Mar 2014; Cold Spring Harbor, NY (Talk)

{\bf Freeberg MA}, Billi AC, and Kim JK. Germline expression, inheritance, and genomic characteristics of {\em Caenorhabditis elegans} 21U-RNAs. 18th International {\em C. elegans} Meeting; Jun 2011; Los Angeles, CA (Poster)

%{\bf Freeberg MA}. Functional Annotation of Non-Coding Elements in the Amphioxus Genome. Saint Vincent College 6th Annual Undergraduate Conference; Apr 2009; Latrobe, PA. (Talk)\\

% {\bf Freeberg MA} and Demirev PA. Bioinformatics Approach to Protein Database Generation for the Identification of Microorganisms by Mass Spectrometry. Saint Vincent College 5th Annual Undergraduate Conference; Apr 2008; Latrobe, PA. (Poster)

% {\bf Freeberg MA} and Sierk ML. Assessment of Homolog Detection by Profile-based Protein Sequence Alignment Methods Against a Structure-based Gold Standard. Duquesne University Annual Summer Undergraduate Research Symposium; Aug 2006; Pittsburgh, PA. (Poster)

\section{\sc Funding and Awards} 
%{\bf University of Michigan}\\
{XSEDE Educational Computational Resource Allocation (2017)}\\
{XSEDE Startup Computational Resource Allocation (2017)}\\
%{Galaxy Community Fund, Travel Award (2017)}\\
%{Rackham Conference Travel Grant (2014)}\\
{Rackham Predoctoral Fellowship (2013-2014)}\\
{NSF Open Data IGERT Fellowship (2010-2013)}\\
{Rackham Graduate Student Research Grant (2010, 2012)}\\
{NIH Bioinformatics Training Grant (2009-2010)}\\

%\vspace{-.2cm}
%{\bf Saint Vincent College}\\
%{Graduated Summa Cum Laude, 2009}\\
%{President's Award Finalist, 2009}\\
%{Outstanding Bioinformatics Student Award, 2009}
%{Who's Who Among Students in American Universities and Colleges   2009}\\
%{Alpha Lambda Delta Academic Honor Society 2006-2009}

\section{\sc Computing and Data Analysis Skills} 
Operating Systems: MacOS X, Linux/Unix \\
Languages: Python, Perl, SQL, Unix shell \\
Statistical Packages: R, Bioconductor \\
%Applications: \LaTeX, MySQL, Galaxy, biomolecule sequence/structure analysis tools, NGS analysis tools and methodologies\\
Applications: JSON/XML, GitHub, \LaTeX, Galaxy, NGS analysis tools and methodologies\\
%Laboratory Techniques: Nanopore sequencing, general molecular biology techniques\\
%Laboratory Techniques: Nanopore sequencing (Oxford Nanopore Technologies), general molecular biology techniques

%\section{\sc University and Community Service}
%%{Volunteered for FEMMES Capstone Science weekend}\\
%%{Judged Pioneer High School Science Fair, 2014}\\
%%{Judged Forsythe Middle School Science Fair, 2014}\\
%{Peer reviewed for {\em Cell Rep},  {\em Epigenetics}, {\em Genome Biol}, {\em Genome Res}, {\em PLoS Biol}, {\em RNA}, and {\em RNA Biol} (2013-2014)}\\
%%{Judged Webster Elementary School Science Fair and Exhibition, 2013-2014}\\
%%{Organized departmental happy hours following student seminars, 2012-2014}\\
%{Participated in departmental student recruiting activities, University of Michigan (2011-2015)}\\
%%{Judged Elementary, Middle, and High School Science Fairs, 2013-2014}

\section{\sc Teaching and Mentoring Experience}
{\bf Open Life Science}, Cambridge, UK\hfill {Aug 2020 - Dec 2020}\\
Mentor for 16-week personal mentorship and cohort-based training program\\
Responsibilities: Mentoring two OLS-2 cohort participants on open practices

{\bf STEM Ambassador}, Cambridge, UK\hfill {Jan 2018 - Present}\\
Ambassador for STEM-related volunteer program\\
Responsibilities: Supporting various public engagement activities including giving talks, demonstrating science experiments, providing career guidance

{\bf Johns Hopkins University}, Baltimore, MD USA\hfill {Jan 2017 - May 2017}\\
Instructor for Advanced Academic Program online course: {\em Bioinformatics: Tools for Genome Analysis}\\
Responsibilities: Created course materials, held office hours, graded assignments

%{\bf Sisters Circle}, Baltimore, MD USA\\
%One-on-one mentor for middle school student\hfill { May 2016 - present}

{\bf Sisters Circle}, Baltimore, MD USA\hfill {May 2015 - Sep 2017}\\
Mentor/tutor for middle school girls\\
Responsibilities: Co-led weekly after-school sessions, tutored math, did 1-on-1 mentoring

{\bf University of Michigan}, Ann Arbor, MI USA\hfill {Jul 2014 - Aug 2014}\\
Mentor for high school student\\
Responsibilities: Designed bioinformatics/genomics research project, taught shell/perl programming

%{\bf Saint Vincent College}, Latrobe, PA USA\\
%Laboratory Assistant for General Chemistry \hfill { Jan - May 2009}\\
%Responsibilities: Held office hours, prepared and supervised laboratory exercises, graded assignments

%Laboratory Assistant for Genes, Cells, and Computers \hfill { Aug - Dec 2008}\\
%Responsibilities: Held office hours, prepared and supervised laboratory exercises, graded assignments

%Tutor for Bioinformatics, Genomics, and Proteomics \hfill { Aug - Dec 2007}\\
%Responsibilities: Held office hours, led study sessions

\end{resume}
\end{document}

